Have you forgotten?' Conversion experiences in shopping lists

### 2017-02-01 lists_conversion_experience.rmd
planning edit

```{r random_basket, echo=FAlSE, cache=TRUE, fig.cap='Random basket'}
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
csvs = list.files('data', pattern = '*.csv',full.names=TRUE)
df = bind_rows(sapply(csvs, read_tsv))
kable(sample_n(df, size=5)$name, col.names='item')
```

@@

```{r arules, cache=TRUE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
options(digits=2)
rules<-apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=F))
rules<-sort(rules, decreasing=TRUE,by="confidence")
inspect(rules[1:5]) 
items = Groceries@itemInfo
```

The association rule-based model for the `Groceries` dataset suggests some of the characteristic ordering practices of 1990s-style data-mining approaches to lists. 
The association between items is expressed in the form of _rules_. These rules, a term derived from decision support literature, define sets of associations between items. As a set theory-based practice, the association rules define likely sets of items or shopping baskets in terms of decreasing probability.   `r inspect(rules[1])` is a stronger association than `r inspect(rules[2])`. So any recommendation in the 'Have You Forgotten' list should probably put them in that order.

>>>>

```{r random-basket, echo=FALSE, cache=TRUE, fig.cap='Random basket'}
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
csvs = list.files('data', pattern = '*.csv',full.names=TRUE)
df = bind_rows(sapply(csvs, read_tsv))
kable(sample_n(df, size=5)$name, col.names='item')
```

@@

```{r arules, cache=TRUE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
options(digits=2)
rules<- apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=F))
rules_sorted <- sort(rules, decreasing=TRUE,by="confidence")
rule1 <- inspect(rules_sorted[1])
rule2 <- inspect(rules_sorted[2])
kable(inspect(rules[1:5]))
items <- Groceries@itemInfo
```

The association rule-based model for the `Groceries` dataset suggests some of the characteristic ordering practices of 1990s-style data-mining approaches to lists. The association between items is expressed in the form of _rules_. These rules, a term derived from older decision support literature, define sets of associations between items. As a set theory-based practice, the association rules define likely sets of items or shopping baskets in terms of decreasing probability. Table \@ref(tab:arules) shows that the first rule has a stronger association than the second. Milk and vegetables is more likely an association than milk and buns.   So any recommendation in the 'Have You Forgotten' list should probably put them in that order.
